### 2021-12-01 plos_latex_template.tex
RJ: Edits to rule 8

% Be more direct
Conferences are among the least accessible spaces that people with disabilities may encounter in professional contexts \cite{priceAccessImaginedConstruction2009}. Even when conferences implement other inclusive practices, the participation of people with disabilities is often overlooked \cite{marks2021meeting}. This is one key aspect where participation in the organizing team allows disabled people to take part in the decisions from the beginning (see rule 3 about the organizing team), as thinking about disability or simulating it are not substitutes for real-life experience \cite{costanzachockDesign2020}. Planning for accessibility requires time and early decision-making \cite{irishIncreasingParticipationUsing2020}. As other aspects of inclusion, dealing with accessibility at the last minute is the recipe for a disastrous conference. If you do not consider accessibility from the conference inception, it is highly likely you will be better off without trying to patch accessibility at the last minute. Key decisions in this respect are hard to correct.

@@

Regardless of the conference format, all platforms (website, chat, conference administration tools) and images used for the communication strategy of the conference should be screen-reader friendly and keyboard accessible, and have alternative text. Any videos should have good-quality captions and a transcript.
The organizing team should provide accessibility guidelines for slides and presentations, encourage their use, and be available for any questions presenters and attendees may have. Slide decks should be made available beforehand, either in webpages or available for download to ensure that everybody can follow their content during the presentations.

@@

%Live captioning or interpretation! and surtitles (Rita) LA: provide live, high-quality (automated captions are often referred to as "craptions"), captioning or simultaneous translation in English for persons who only speak English. After all, captions and simultaneous translations are common place in the audiovisual industry and your conference audience will likely be already familiar with this if they ever watched a movie from a non-English speaking country.

@@

%Rocío: Main idea: Include people in your communication 
The communication strategy of your conference should aim to increase the number and diversity of participants, and be inclusive by design.
Actively reach out and promote the conference to people who have been systematically excluded. 
Publish the diversity statement, the Code of Conduct, the accessibility guidelines, and  options for financial support (see rule 9 about financial resources), to emphasize that everybody is welcome in the event.
Try to come up with creative ways to show that everyone is seen, respected, and welcome. For example, useR! 2021 created a mascot for the conference wearing different scarfs reflecting folks from different groups that the conference wanted to reach (Fig. 2). 
The diverse organizing team should be able to help deciding which languages to emphasize and which social media platforms to utilize in the promotion of the conference (e.g. Twitter, Facebook, LinkedIn, conference website, mailing lists).

%lA: in case it is not mentioned later: If your budget does not allow to accommodate everyone, at a bare minimum, you should inform potential attendant which accommodations you do provide and which you will not. This will help everyone to know up-front what to expect and save their time if your conference does not accomodate their needs adequately.%ast: responsible communication!
%Rocío: Main idea: Use inclusive language
Inclusive language--language free from words, phrases or tones that reflect prejudiced or discriminatory views of particular people or groups--should be used in all communications \cite{hallDesigningDiversityInclusion2019}. 
Make the effort to teach yourself the vocabulary about disabilities, racialized groups, and gender and sexual orientations. %
Do not expect minoritized people to teach you--it's not their role--, and accept feedback without being offended.
Inclusive language also encompasses avoidance of excessive and too specific technical jargon and acronyms. 
%
% links, examples, this changes with the context
%practice: create a standards in inclusive language for your community, to build collective knowledge than can be passed to

% Rocío: could add some ideas from here 
% https://www.science.org.au/files/userfiles/support/emcr/documents/one-page-summary-emcr-improving-diversity-web.pdf

>>>>

% Be more direct
Conferences are among the least accessible spaces that people with disabilities may encounter in professional contexts \cite{priceAccessImaginedConstruction2009}. Even when conferences implement other inclusive practices, the participation of people with disabilities is often overlooked \cite{marks2021meeting}. This is one key aspect where participation in the organizing team allows disabled people to take part in the decisions from the beginning (see rule 3 about the organizing team), as thinking about disability or simulating it are not substitutes for real-life experience \cite{costanzachockDesign2020}. Planning for accessibility requires time and early decision-making \cite{irishIncreasingParticipationUsing2020}. As other aspects of inclusion, dealing with accessibility at the last minute is the recipe for a disastrous conference. If you do not consider accessibility from the conference inception, it is highly likely that you will be better off without trying to patch accessibility at the last minute. Key decisions in this respect are hard to correct.

@@

Regardless of the conference format, all platforms (website, chat, conference administration tools) and images used for the communication strategy of the conference should be screen-reader friendly and keyboard accessible, and have alternative text. Every video should have good-quality (not automated) captions and a transcript; live presentations should have good-quality captions too. 
Provide accessibility guidelines for slides and presentations, encourage their use, and be available for any questions presenters and attendees may have. Slide decks should be made available beforehand, either in webpages or available for download to ensure that everybody can follow their content during the presentations.

@@

%LA: provide live, high-quality (automated captions are often referred to as "craptions"), captioning or simultaneous translation in English for persons who only speak English. After all, captions and simultaneous translations are common place in the audiovisual industry and your conference audience will likely be already familiar with this if they ever watched a movie from a non-English speaking country.

@@

%Rocío: Main idea: Include people in your communication 
The communication strategy of your conference should aim to increase the number and diversity of participants, and be inclusive by design.
Actively reach out and promote the conference to people who have been systematically excluded. 
Publish the diversity statement, the Code of Conduct, the accessibility guidelines, and  options for financial support (see rule 9 about financial resources), to emphasize that everybody is welcome in the event.
Try to come up with creative ways to show that everyone is seen, respected, and welcome. For example, useR! 2021 created a mascot for the conference wearing different scarves reflecting folks from different groups that the conference wanted to reach (Fig. 2). 
The diverse members of your team should be able to decide which languages to emphasize and which social media platforms to utilize in the promotion of the conference (e.g. Twitter, Facebook, LinkedIn, conference website, mailing lists).
Be transparent with potential attendees and communicate limitations of your conference to let them know what to expect, and ways in which you will try to mitigate these issues. For instance, inform if the conference platform is not completely screen-reader friendly, but you are offering personalized help to navigate it, or if captions will be available for some talks but not all. %ast: responsible communication!

%Rocío: Main idea: Use inclusive language
Inclusive language--language free from words, phrases or tones that reflect prejudiced or discriminatory views of particular people or groups--should be used in all communications \cite{hallDesigningDiversityInclusion2019}. 
Become familiar with the terminology used for disabilities, racialized groups, and gender and sexual orientations, and with the terms that should be avoided. %
Do not expect minoritized people to teach you--it's not their role--, and accept feedback without being offended.
Inclusive language also encompasses avoidance of excessive and too specific technical jargon and acronyms. 
%
% links, examples, this changes with the context
%practice: create a standards in inclusive language for your community, to build collective knowledge than can be passed to
